Advances in Robust Positive Invariant Set Computation

### 2015-03-15 draft.tex
Revised changes.

\usepackage{graphics}
\usepackage{epsfig}
% \usepackage{mathptmx}
% \usepackage{times}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{cite}
\usepackage{lpic}
% \usepackage{blkarray}
\usepackage{mathrsfs}

@@

\author{Rainer M. Schaich\textsuperscript{\dag} %
         and Mark Cannon\textsuperscript{\dag,\ddag}%
\thanks{\textsuperscript{\dag} Department of Engineering Science, University of Oxford, OX1 3PJ.}%
\thanks{\textsuperscript{\ddag} Corresponding author, 
        \texttt{mark.cannon@eng.ox.ac.uk}.}
}

@@

\section{Introduction}
Ever since the introduction of disturbance invariant sets in~\cite{Glover:1971}, the analytic
properties of these sets have been fairly well studied, see~\cite{blanchini:2007}. Here by disturbance
invariant sets we mean set $\mathscr X$ containing initial conditions for the perturbed linear system
\begin{equation}\label{eq:system:equation}
	x^+ = \Psi x + v,
\end{equation}
where $\Psi$ is Hurwitz, $x,x^+\in\mathbb R^n$ the state and the successor state, and where 
$v\in\mathscr V$ denotes the perturbation, such that the successor state is contained in the 
disturbance invariant $x^+\in\mathscr X$ set for all possible realisations of the 
perturbation $v\in\mathscr V$. That is summarised in the implicit definition
\begin{equation}\label{eq:definition:mrpi:set:state:dependent}
	\mathscr X = \{x:\Psi x + v\in\mathscr X\; \forall v\in\mathscr V\}.
\end{equation}
These sets are known as robust positive invariant (RPI) sets, for obvious reasons we are interested 
the largest such set, i.e. the set containing all other RPI sets $\mathscr X\subseteq\mathcal X^\infty$,
this set is called the maximal robust positive invariant (mRPI) set. Even though analytical properties
of these sets were derived early after their introduction, it took more than two decades until algorithms
were introduced to numerically compute mRPI sets~\cite{DeSantis:1994,Kolmanovsky:1995,Blanchini:1994}. Earlier algorithms
did not guarantee finite determinability of $\mathcal X^\infty$, see e.g.~\cite{Blanchini:1990}, or 
did not guarantee to produce the maximal RPI set, e.g.~\cite{Blanchini:1991}. 
%
In the afore mentioned algorithms the perturbation was considered to belong to a fixed compact set, in this paper
we consider sets that vary with parameters. First we consider the set of disturbances to be state dependent, i.e.
\begin{equation}\label{eq:PWA:distrubance:set}
	\mathcal V(x) = \left\{v: Gv\leq\max\{{\bf{1}},H^x x\}\right\},
\end{equation}
where the maximum is understood to be element-wise. This means that in the first part of the paper
we will discuss the computation of $\mathcal X^\infty$ for the case where $\mathscr V=\mathcal V(x)$.
The case where the disturbance depends on the state has been studied analytically before but not 
extensively, see~\cite{Kuntsevich:1995}.

The second case we consider is the case of a scaled set of disturbance, i.e.
\begin{equation}
  \mathcal V(\theta) = \{v:Gv\leq(1+\theta){\bf{1}}\},
\end{equation}
with $\theta>-1$. To distinguish the resulting sets from regular mRPI sets we use $\mathcal Z^\infty$
to emphasise that $\mathcal Z^\infty$ itself is not an mRPI set, however by fixing $\theta=\hat\theta$ the
set $\mathcal Z^\infty\vert_{\hat\theta}$ is an mRPI set. To our best knowledge, this setup has not been 
presented in the literature.

The remainder of this paper is structured: In section~\ref{sec:parametrically:convex:set:operations} we
introduce the notion of \emph{parametric convexity} and of its general implications, this is necessary 
for the convexity of the mRPI set. The algorithm to compute the mRPI set for state dependent disturbance
constraints is presented in section~\ref{sec:state:dep:mrpi}, we also prove its finite determinability.
In section~\ref{sec:first:example} we demonstrate the algorithm using a numerical exemplary system, a
levitating ball setup. The case of scaled disturbance constraints is discussed in section~\ref{sec:mRPI:parametrised}
where the algorithm for the parametrised mRPI set as well as the proof for its finite determinability
are also presented. Section~\ref{sec:second:example} illustrates the use of parametrised mRPI sets using
again the levitating ball example and illustrating some of possible robustness analyses of the parametrised
mRPI sets with a numerical example. The paper is concluded in section~\ref{sec:conclusions}.

@@

      Let $X\subseteq\mathbb R^n$ and $Y\subseteq\mathbb R^m$ and $T:X\rightarrow Y$, $X\ni s\mapsto T(s)\subset Y$ be a 

@@

Let $S\subseteq X$ and let $T:X\to X$ be a continuous point-to-set map,

@@

@@

@@

      Let $S\subseteq X$ be a convex set and let $T:X\rightarrow X$ be a parametrically convex point-to-set

@@

    In the given setup we consider a point-to-set map defined by
    \begin{equation}\label{eq:definition:disturbance:set}
      \mathcal V(x) = \{v:\,G v \leq H(x)\}
    where $H$ is elementwise convex in $x$, so that 

@@

    $\lambda\in[0,1]$.  For such sets we have the following result.

@@

      $\mathcal V (x)$ defined in~\eqref{eq:definition:disturbance:set} is parametrically convex.

@@

and~\ref{thm:convex:parametric:set} imply that the difference of a convex set and 
$\mathcal V(x)$ is a convex set.

@@

V(x)$ is as defined in~\eqref{eq:PWA:distrubance:set}, then $\mathcal X\ominus\mathcal V(\mathcal X)$ is 

@@

the computation of the mRPI set~\eqref{eq:definition:mrpi:set:state:dependent}.

@@

\section{Maximal Robust Positive Invariant Sets for State Dependent Disturbance}\label{sec:state:dep:mrpi}
In this section we describe an iterative algorithm to compute the mRPI 
set~\eqref{eq:definition:mrpi:set:state:dependent} for a linear system~\eqref{eq:system:equation}.
For this notice that the set $\mathcal V(x)$ can be represented as the convex hull of its vertices 
$\mathcal V(x) = \conv\{v_i(x)\}$. Since ${\mathcal{V}}(x)$

@@

The set $\mathcal X^\infty$ as defined in~\eqref{eq:definition:mrpi:set:state:dependent} 

@@

$x\in\mathcal X^\infty$ and $v\in\mathcal V(x)$, to compute the mRPI set we start from a given set
$\mathcal X_0 = \{x:\;\genmat_{0,i}x\leq \genvec_{0,i}\,\forall i\in\mathcal I_0\}$, e.g.
the system constraints, and 
\emph{cut off} all points that do not satisfy the invariance condition in one step, two steps, 
etc. until only points satisfying the conditions are left. I.e. we iteratively introduce 
constraints that cut off all points for which the successor state can lie outside 

@@

	v_{l,i}^\ast(x)=\begin{split}\max& \genmat_{0,i}\Psi^{l-1}v_j(x)\\ j&\end{split}
	 = \begin{split}&\max \genmat_{0,i}\Psi^{l-1}v \\ &v\in\mathcal V(x)\end{split}\\
	= \begin{split}&\max \genmat_{0,i}\tilde v\\ &\tilde v\in \Psi^{l-1}\mathcal V(x) \end{split}

@@

\begin{thm}\label{thm:finite:mRPI:set:state:dependable}

@@

-\Gamma x\leq{\bf{1}}\}$, let the pair $(\Psi,\Gamma)$ be observable and let $\mathcal V(\mathcal X_0)$ be bounded, 
then $\mathcal X_N\subseteq \mathcal X_{N+1}$ for a finite $N$. Hence the mRPI set $\mathcal X^\infty 
=\mathcal X_N$ is a finite polytope.

@@

@@

has more than rank one. To see that $D_k$ grows exponentially we use that $\mathcal V(\mathcal X_0)$
is bounded, let $K_1$ denote the smallest ball that contains $\mathcal V(\mathcal X_0)$ and let

@@

D_k = \underbrace{\Psi^{-k}\mathcal X_0}_{(\ast)} \ominus \underbrace{\left(\bigoplus_{i\leq k-1} 
\Psi^i\mathcal V(\mathcal X_k)\right)}_{(\ast\ast)}.

@@

$\bar\lambda^{-l}K_1\subseteq\Psi^{-l} K_1 \subseteq \Psi^{-l}\mathcal X_0 = (\ast)$
which implies exponential growth of $D_k$ as long as $(\ast\ast)$ is bounded.
To bound $(\ast\ast)$ we use $(\ast\ast)\subseteq \oplus_{i\leq k-1} \bar\lambda^i K_2 \subseteq
\frac{1}{1-\bar\lambda} K_2$. This concludes the proof: We proved that $D_k$ grows exponentially,

@@

In this section we discuss the calculation of the mRPI set for a simplified model of the levitating

@@

and the input matrix $B = T_s \frac{\partial f}{\partial u}(\hat x,\hat u)$. In order to obtain a 
representation of additive disturbances depending on the state and input like~\eqref{eq:definition:disturbance:set}
we use the mean-value theorem for vector valued functions:

@@

\begin{thm}\label{thm:mean:value:theorem}

@@

This implies that for any linearised state $\tilde x$ we obtain the expression

@@

of $H^x$ and $H^u$ requires solving a nonlinear integral. Assume that inside given compact system
constraints $\mathcal X$ and $\mathcal U$ we had extremal values of $H^x$ and $H^u$, i.e.

@@

finding the extremal values of $(H^x,H^u)$ can not be done easily, so for the example of the 
levitating ball we use the parameters: $Ts=30ms, C=1, m=100g, \hat x_1 = 50mm$ and $\mathcal X=\{x:

@@

Using 25 samples of $(H^x,H^u)$ we obtain the invariant set shown in figure~\ref{fig:mrpi:set:levitating:ball},

@@

@@

\label{fig:mrpi:set:levitating:ball}

@@

\section{Maximal Robust Positive Invariant Sets for Parametrised Disturbance}\label{sec:mRPI:parametrised}

@@

In this section we describe the computation of the mRPI set for~\eqref{eq:system:equation}

@@

$\mathcal U({\bf{\alpha}}) = \{u: Fu\leq\left(I+\text{diag}(\alpha_1,\dots,\alpha_p)\right){\bf{1}}\}$, 
this can be used to study closed loop systems subject to a given feedback controller.

@@

In the following we describe an algorithm to compute the mRPI set $\mathcal Z^\infty$ contained in 

@@

As in the state dependent case we iteratively introduce constraints \emph{cutting off} points

@@

\begin{array}{rl}
\max&\mathcal F_i \Psi^l v \\ \text{s.t.}&v\in\bar{\mathcal{V}}
\end{array} = 
\begin{array}{rl}
\max&\mathcal F_i \tilde  v \\ \text{s.t.}&\Psi^{-l} \tilde v\in\bar{\mathcal{V}}
\end{array} = 
\begin{array}{rl}
\max&\mathcal F_i v \\ \text{s.t.}& \tilde v\in\Psi^l\bar{\mathcal{V}}

@@

$\bar{\mathcal{V}}=\mathcal V(0)$ for notational convenience. So that for any fixed $\hat\theta>-1$

@@

The iteration terminates when $Z_k\subseteq Z_{k+1}$. Like in section~\ref{sec:state:dep:mrpi}

@@

for a finite $N$. Hence the mRPI set $\mathcal Z^\infty = Z_N$ is a finite polyhedron.

@@

@@

The argumentation in this completely analogue to the one in Lemma~\ref{thm:finite:mRPI:set:state:dependable}.

@@

observability argument as in Lemma~\ref{thm:finite:mRPI:set:state:dependable}.

@@

In this section we compute the mRPI set for the levitating ball exemplary system presented in 
section~\ref{sec:first:example} as well as for a direct torque fed pendulum to illustrate both

@@

the system analysis tool that is the parametrised mRPI set. First we present the parametrised mRPI

@@

on the effect of nonlinearities on each state, i.e. a constant version 
of~\eqref{eq:definition:element:wise:constraints:on:nonlinearities}. Using the same constraint set 

@@

a scaling parameter $\alpha$ such that $\mathcal U(0)=\mathcal U$. For this setup we obtain the mRPI

@@

positive entries, i.e. increasing $\alpha$ will enlarge the parametrised mRPI set $\mathcal Z^\infty\vert_{\alpha_1}

@@

First we want to compare the mRPI set $\mathcal X^\infty$ obtained with state dependent disturbance 
constraints with the parametrised one $\mathcal Z^\infty$. To do this we compute the scaling parameter 
$\alpha_{\min}$ such that $\mathcal X^\infty\subseteq\mathcal Z^\infty\vert_{(0,\alpha_{\min})}$.
We can do this by solving $m_\infty$ linear programs
%
%
\[
	\gamma_i^\ast = \left\{\begin{split}
	\max& \;\Lambda_i^x x\\
	\text{s.t.}& \;x\in\mathcal X^\infty
	\end{split}
	\right.
\]
%
%
The minimal value for $\alpha_{\min}$ is then given by the maximal $\alpha$ satisfying $\gamma_i^\ast + 
\Lambda_i^\theta\cdot 0 + \Lambda_i^\alpha \alpha \leq \lambda_i$. Solving this we obtain the 
minimal value $\alpha_{\min} = 1.7555$ and the mRPI sets shown in Figure~\ref{fig:minimal:scaling:comparison:mRPIs}.
Caution is advised when interpreting $\alpha>0$, since the system is nonlinear extrapolations bare very
little insight, the only information we can safely extract is that the current set of inputs $\mathcal U(0)=\mathcal U$ 
is not large enough to cope with the perturbation set containing given by upper bounds of the nonlinear effects.
%
%
\begin{figure}
\begin{lpic}{minimalAlphaForConstantDisturbance(.65,)}
{\tiny
\lbl[r]{7,87;$1.5$}
\lbl[r]{7,69;$1$}
\lbl[r]{7,51;$0.5$}
\lbl[r]{7,34;$0$}
\lbl[r]{7,16;$-0.5$}
\lbl[t]{15,2;$-0.06$}
\lbl[t]{27,2;$-0.05$}
\lbl[t]{39,2;$-0.04$}
\lbl[t]{51,2;$-0.03$}
\lbl[t]{63,2;$-0.02$}
\lbl[t]{75,2;$-0.01$}
\lbl[t]{89,2;$0$}
\lbl[t]{100,2;$0.01$}
\lbl[t]{113,2;$0.02$}
}
{\footnotesize
\lbl[r]{5,45,90;$\tilde x_2$}
\lbl[t]{121,3;$\tilde x_1$}
}
\lbl[l]{93,32;$\longleftarrow\mathcal X^\infty$}
\lbl[r]{68,43;$\mathcal Z^\infty\vert_{(\alpha_{\min},0)}\longrightarrow$}
\end{lpic}
\caption{Minimal scaling for mRPI set computed for constant disturbance which contains
 mRPI set for piecewise affine disturbances is $\alpha=1.7555$. Note that since the nonlinearities of the system
 dynamics are not symmetrical around the equilibrium the mRPI set with fixed constraints on the perturbation
 is non-symmetric.}
 \label{fig:minimal:scaling:comparison:mRPIs}
\end{figure}

In the second example we compute the parametrised mRPI set for the system

@@

\underbrace{\left(\begin{array}{cc} 1 & 2 \\ 2 & 1 \end{array}\right)}_D w

@@

@@

(\theta)\wedge \alpha,\theta>-{\bf{1}}\right\}$, with $K$ and $K_w$ being the solution to the semidefinite program

@@

We use $Q = \text{diag}(2,1)$ and $R = I$. Using these numerical values we determine the mRPI set 
$\mathcal Z^\infty$ after 22 iterations, it has 61 facets. Notice that in addition to the sign of 
the sensitivity of the mRPI set on $\alpha$ we know that since we introduced each facet of $\mathcal Z$
to depend only on one $\alpha_i$, since the algorithm does not change the elements corresponding to $\alpha$
and due to orthogonality two facets depending on different elements of $\alpha$ can not be reduced to 
one facet depending on both. I.e. $\Lambda^\alpha$ has no more than one entry per row. We can therefore 
compute which $\alpha_i$ will change the mRPI set the most. This can be done by element wise calculating

@@

Analogue to the first example we might want to know how much disturbance the closed loop system can 

>>>>

\usepackage{graphics}
\usepackage{epsfig}
% \usepackage{mathptmx}
% \usepackage{times}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{cite}
\usepackage{lpic}
% \usepackage{blkarray}
\usepackage{mathrsfs}
\usepackage{todonotes}

@@

\author{Rainer M. Schaich\textsuperscript{\dag} %
         and Mark Cannon\textsuperscript{\dag,\ddag}%
\thanks{\textsuperscript{\dag} Department of Engineering Science, University of Oxford, OX1 3PJ.}%
\thanks{\textsuperscript{\ddag} Corresponding author, 
        \texttt{mark.cannon@eng.ox.ac.uk}.}
}
\newcommand{\note}[1]{\todo[inline]{#1}}

@@

\section{Introduction}
Ever since the introduction of disturbance invariant sets in~\cite{Glover:1971}, the analytic
properties of these sets have been fairly well studied, see~\cite{blanchini:2007}. Here by disturbance
invariant sets we mean a subset of the state constraint set $\mathscr X\subseteq\mathcal X_0\subseteq\mathbb R^n$ 
containing initial conditions for the perturbed linear system
\begin{equation}\label{eq:system:equation}
	x^+ = \Psi x + v,
\end{equation}
where $\Psi$ is Hurwitz, $x,x^+\in\mathcal X_0$ the state and the successor state, and where 
$v\in\mathscr V$ denotes the perturbation, such that the successor state is contained in the 
disturbance invariant set $x^+\in\mathscr X$ for all possible realisations of the 
perturbation $v\in\mathscr V$. That is summarised in the implicit definition
\begin{equation}\label{eq:definition:MRPI:set:state:dependent}
	\mathscr X = \{x:\Psi x + v\in\mathscr X\; \forall v\in\mathscr V\}.
\end{equation}
These sets are known as robust positive invariant (RPI) sets. In many applications we are interested in the largest such
set $\mathcal X^\infty$, i.e. the set containing all other RPI sets $\mathscr X\subseteq\mathcal X^\infty$,
this set is called the maximal robust positive invariant (MRPI) set. These sets are used e.g. as terminal regions in 
robust model predictive control. Even though analytical properties
of these sets were derived early after their introduction, it took more than two decades until algorithms
were introduced to numerically compute MRPI sets~\cite{DeSantis:1994,Kolmanovsky:1995,Blanchini:1994}. 
\note{You commented 'check', I didn't know what that meant.}
Earlier algorithms
did not guarantee finite determinability of $\mathcal X^\infty$, see e.g.~\cite{Blanchini:1990}, or 
did not guarantee to produce the maximal RPI set, e.g.~\cite{Blanchini:1991}. 
%
In the afore mentioned algorithms the perturbation was considered to belong to a fixed compact set, in this paper
we consider sets that vary with parameters. First we consider the set of disturbances to be state dependent, e.g.
\begin{equation}\label{eq:PWA:distrubance:set}
	\mathcal V(x) = \left\{v: Gv\leq H(x)\right\},
\end{equation}
where $H(x)$ is a piecewise affine function. This means that in the first part of the paper
we discuss the computation of $\mathcal X^\infty$ for the case where $\mathscr V=\mathcal V(x)$.
The case where the disturbance depends on the state has been studied analytically before but not 
extensively, see~\cite{Kuntsevich:1995}. These kind of disturbance constraints can be used to
account for linearisation errors, as will be shown in section~\ref{sec:first:example}, but can also
be used to treat multiplicative uncertainty.

The second case we consider is the case of a scaled set of disturbance, i.e.
\begin{equation}
  \mathcal V(\theta) = \{v:Gv\leq(1+\theta){\bf{1}}\},
\end{equation}
with $\theta>-1$. To distinguish the resulting sets from regular MRPI sets we use $\mathcal Z^\infty$
to emphasise that $\mathcal Z^\infty$ itself is not an MRPI set, however by fixing $\theta=\hat\theta$ the
set $\mathcal Z^\infty\vert_{\hat\theta}$ is an MRPI set. To our best knowledge, this setup has not been 
presented in the literature. This type of disturbance constraints can be used to study the sensitivity of
the MRPI set to changes in the disturbance \emph{strength}.

The remainder of this paper is structured: In section~\ref{sec:parametrically:convex:set:operations} we
introduce the notion of \emph{parametric convexity} and of its general implications, this is sufficient 
for the convexity of the MRPI set. The algorithm to compute the MRPI set for state dependent disturbance
constraints is presented in section~\ref{sec:state:dep:MRPI}, we also prove its finite determinability.
In section~\ref{sec:first:example} we demonstrate the algorithm using a numerical exemplary system, a
levitating ball setup. The case of scaled disturbance constraints is discussed in section~\ref{sec:MRPI:parametrised}
where the algorithm for the parametrised MRPI set as well as the proof for its finite determinability
are also presented. Section~\ref{sec:second:example} illustrates the use of parametrised MRPI sets using
again the levitating ball example and illustrating some of possible robustness analyses of the parametrised
MRPI sets with a numerical example. The paper is concluded in section~\ref{sec:conclusions}.

In the remainder of this paper we use the notion of a polyhedra for sets that can be represented as
the intersection of a finite number of halfspaces, polytopic sets for bounded polyhedral.
By ${\bf{1}}$ we denote the column vector of ones in appropriate dimension, $\wedge$ denotes the logical and. 

@@

      Let $X\subseteq\mathbb R^n, Y\subseteq\mathbb R^m$, let $\mathcal P(Y)$ denote the power set of $Y$ 
      and $T:X\rightarrow \mathcal P(Y)$, $X\ni s\mapsto T(s)\subset Y$ be a 

@@

Let $S\subseteq X$ and let $T:X\to\mathcal P(X)$ be a continuous point-to-set map,

@@

      \begin{equation}\label{eq:definition:parametric:pontryagin:difference}

@@

    Notice that for constant maps $T$
    definition~\eqref{eq:definition:parametric:pontryagin:difference} is equivalent to the 
    well known Pontryagin difference.

@@

      Let $S\subseteq X$ be a convex set and let $T:X\rightarrow\mathcal P(X)$ be a parametrically convex point-to-set

@@

  Consider a point-to-set map defined by~\eqref{eq:PWA:distrubance:set}
    where, for now, $H$ is elementwise convex in $x\in \mathscr X\subseteq\mathbb R^n$, so that 

@@

    $\lambda\in[0,1]$ and $x_1, x_2\in X$.  For such sets we have the following result:

@@

      The point-to-set map $\mathcal V (x)$ defined in~\eqref{eq:PWA:distrubance:set} is parametrically 
      convex for all $x\in X.$

@@

and~\ref{thm:convex:parametric:set} imply that the parametric Pontryagin difference between a convex set $\mathcal X$ and 
the point-to-set map $\mathcal V(x)$, i.e. $\mathcal X\ominus \mathcal V(\mathcal X)$, is a convex set.

@@

V(x)$ is point wise polytopic, then $\mathcal X\ominus\mathcal V(\mathcal X)$ is 

@@

the computation of the MRPI set~\eqref{eq:definition:MRPI:set:state:dependent}.

@@

\section{Maximal Robust Positive Invariant Sets for State Dependent Disturbance}\label{sec:state:dep:MRPI}
In this section we describe an iterative algorithm to compute the MRPI 
set~\eqref{eq:definition:MRPI:set:state:dependent} for a linear system~\eqref{eq:system:equation} subject to disturbance
$v\in\mathcal V(x)$ where $\mathcal V(x)$ is defined as in~\eqref{eq:PWA:distrubance:set} with a piecewise affine $H(x)$.
Notice that the set $\mathcal V(x)$ is pointwise polytopic for finite $x\in\mathcal X_0$ and can hence be represented as the 
convex hull of its vertices $\mathcal V(x) = \conv\{v_i(x)\}$. Since ${\mathcal{V}}(x)$

@@

The set $\mathcal X^\infty$ as defined in~\eqref{eq:definition:MRPI:set:state:dependent} 

@@

$x\in\mathcal X^\infty$ and $v\in\mathcal V(x)$. To compute the MRPI set we start from the given 
state constraint set
$\mathcal X_0 = \{x:\;\genmat_{0,i}x\leq \genvec_{0,i}\,\forall i\in\mathcal I_0\}$ and 
\emph{cut off} all points that do not satisfy the invariance condition in $k$ steps, $k\in\mathbb N$. 
So that all points remaining satisfy the invariance condition~\eqref{eq:definition:MRPI:set:state:dependent}. 
I.e. we iteratively introduce 
constraints that separate all points for which the successor state can lie outside 

@@

	v_{l,i}^\ast(x)=\max_j \genmat_{0,i}\Psi^{l-1}v_j(x)\\
	 = \begin{array}{rl} \max& \genmat_{0,i}\Psi^{l-1}v \\ \text{s.t.}& v\in\mathcal V(x)\end{array}
	 = \begin{array}{rl} \max& \genmat_{0,i}\tilde v\\ \text{s.t.}& \tilde v\in \Psi^{l-1}\mathcal V(x) \end{array}

@@

\begin{thm}\label{thm:finite:MRPI:set:state:dependable}

@@

-\Gamma x\leq{\bf{1}}\}$, let the pair $(\Psi,\Gamma)$ be observable and let $\mathcal V(x)$ be defined by~\eqref{eq:PWA:distrubance:set}
with a piecewise affine $H$, 
then $\mathcal X_N\subseteq \mathcal X_{N+1}$ for a finite $N$. Hence the MRPI set $\mathcal X^\infty 
=\mathcal X_N$ is a polytope.

@@

Notice that with~\eqref{eq:set:iteration:state:dependent:constraints} it is easy to see that in early
iterations the parametric Pontryagin difference can yield the empty set. The empty set however is
an admissible polytope, i.e. an admissible MRPI set. For the remainder of this proof we assume
that the MRPI set is non-empty. For this notice that on any compact set $\mathcal S\subset\mathbb R^n$ we
have $\bigcup_{s\in\mathcal S}\mathcal V(s)$ is compact.

@@

has more than rank one. To see that $D_k$ grows exponentially we use that $\mathcal V(\mathcal X_{n+1})$
is bounded, let $K_1$ denote the smallest ball that contains $\mathcal V(\mathcal X_{n+1})$ and let

@@

D_k = \underbrace{\Psi^{-k}\mathcal X_0}_{(i)} \ominus \underbrace{\left(\bigoplus_{i\leq k-1} 
\Psi^i\mathcal V(\mathcal X_k)\right)}_{(ii)}.

@@

$\bar\lambda^{-l}K_1\subseteq\Psi^{-l} K_1 \subseteq \Psi^{-l}\mathcal X_0 = (i)$
which implies exponential growth of $D_k$ as long as $(ii)$ is bounded. Recall that we assume
that the MRPI set is non-empty.
Hence, to bound $(ii)$ we use $k\geq n+1$ where $(ii)\subseteq \oplus_{i\leq k-1} \bar\lambda^i K_2 \subseteq
\frac{1}{1-\bar\lambda} K_2$ holds. This concludes the proof: We proved that $D_k$ grows exponentially,

@@

In this section we discuss the calculation of the MRPI set for a linearised simplified model of the levitating

@@

and the input matrix $B = T_s \frac{\partial f}{\partial u}(\hat x,\hat u)$. 
Notice that using a non-autonomous model does not affect our analysis since we analyse the closed loop system
governed by a linear state feedback controller $u=Kx$. To cope with disturbance optimally we use $K$ 
being the solution to robust Lyapunov condition $V(x)-V((A+BK)x+Dw)\leq \gamma^2w^Tw$ with $V(x)=x^T P x\geq0$, i.e.
$x^TPx - ((A+BK)x+Dw)^TP((A+BK)x+Dw)\geq x^T(Q+K^TRK)x -\gamma^2 w^Tw$ for a minimised $\gamma^2$, 
see e.g.~\cite{Boyd:94}.
In order to obtain a 
representation of additive disturbances depending on the state and input like~\eqref{eq:PWA:distrubance:set}
we use the mean-value theorem for vector valued functions, see e.g.~\cite{Apostol:1974}:

@@

\begin{thm}[Mean Value Theorem]\label{thm:mean:value:theorem}

@@

This implies that for any state $\tilde x$ of linearised we obtain the expression

@@

of $H^x$ and $H^u$ requires solving a nonlinear integral. Assume that
for $x\in\mathcal X$ and $u\in\mathcal U$, where $\mathcal X$ and $\mathcal U$ are compact
sets, we had extremal values of $H^x$ and $H^u$, i.e.

@@

finding the extremal values of $(H^x,H^u)$ can not be done easily.
To obtain values for $(H^x_k,H^u_k)$ we sample $\mathcal X\times\mathcal U$ and evaluate the integral 
expressions defining $(H^x_k,H^u_k)$ pointwise. For this we use the numerical values for the example of the 
levitating ball: $Ts=30ms, C=1, m=100g, \hat x_1 = 50mm$ and $\mathcal X=\{x:

@@

Using a total of 25 samples for the computation of $(H^x,H^u)$ we obtain the invariant set shown in figure~\ref{fig:MRPI:set:levitating:ball},

@@

The algorithm terminates after 3 iterations.

@@

\label{fig:MRPI:set:levitating:ball}

@@

\section{Maximal Robust Positive Invariant Sets for Parametrised Disturbance}\label{sec:MRPI:parametrised}

@@

In this section we describe the computation of the MRPI set for~\eqref{eq:system:equation}

@@

$\mathcal U({\bf{\alpha}}) = \{u: Fu\leq\left(I+\text{diag}(\alpha_1,\dots,\alpha_p)\right){\bf{1}}\}$.
The necessity of uniform scaling of the disturbance constraints is due to a finesse we use to avoid
solving multiparametric linear programs in every substep of the proposed iteration.
A representation of the MRPI set of a system parametrised with respect to a scaling parameter allows us
to study the system's sensitivity to \emph{stronger/weaker} disturbance, the sensitivity to input 
constraints can be useful to choose particular actuators.

@@

In the following we describe an algorithm to compute the MRPI set $\mathcal Z^\infty$ contained in 

@@

As in the state dependent case we iteratively introduce constraints \emph{separating} points

@@

\small
\begin{array}{rlcrlcrl}
\max&\mathcal F_i \Psi^l v &=& \max&\mathcal F_i \tilde  v &=& \max&\mathcal F_i v \\ 
\text{s.t.}&v\in\bar{\mathcal{V}} & & \text{s.t.}&\Psi^{-l} \tilde v\in\bar{\mathcal{V}} & &
\text{s.t.}& \tilde v\in\Psi^l\bar{\mathcal{V}}

@@

where $\bar{\mathcal{V}}=\mathcal V(0)$ for notational convenience. For any fixed $\hat\theta>-1$

@@

The iteration terminates when $Z_k\subseteq Z_{k+1}$. As in section~\ref{sec:state:dep:MRPI}

@@

for a finite $N$. Hence the MRPI set $\mathcal Z^\infty = Z_N$ is a finite polyhedron.

@@

\note{You wrote to highlight $\mathcal V(0)$ being bounded was an assumption. It is necessary so I 
don't know what to do with this.}

@@

The proof is, completely analogue to the proof of Lemma~\ref{thm:finite:MRPI:set:state:dependable}.

@@

observability argument as in Lemma~\ref{thm:finite:MRPI:set:state:dependable}.

@@

In this section we compute the MRPI set for the levitating ball example system presented in 
section~\ref{sec:first:example} as well as for a purely numerical model to illustrate both

@@

the system analysis tool that is the parametrised MRPI set. First we present the parametrised MRPI

@@

on the effect of nonlinearities on each state, i.e. a fixed set containing the set $\mathcal V(x,u)$ 
in~\eqref{eq:definition:element:wise:constraints:on:nonlinearities} for all $(x,u)\in\mathcal X\times\mathcal U$. 
Using the same constraint set 

@@

a scaling parameter $\alpha$ such that $\mathcal U(0)=\mathcal U$ for $\alpha=0$. For this setup we obtain the MRPI

@@

positive entries, i.e. increasing $\alpha$ will enlarge the parametrised MRPI set $\mathcal Z^\infty\vert_{\alpha_1}

@@

First we want to compare the MRPI set $\mathcal X^\infty$ obtained with state dependent disturbance 
constraints with the parametrised one $\mathcal Z^\infty$. To do this we compute the scaling parameter 
$\alpha_{\min}$ such that $\mathcal X^\infty\subseteq\mathcal Z^\infty\vert_{(\theta=0,\alpha=\alpha_{\min})}$.
We can do this by solving $m_\infty$ linear programs
%
%
\[
	\gamma_i^\ast = \left\{\begin{split}
	\max& \;\Lambda_i^x x\\
	\text{s.t.}& \;x\in\mathcal X^\infty
	\end{split}
	\right.
\]
%
%
The minimal value for $\alpha_{\min}$ is then given by the maximal $\alpha$ satisfying $\gamma_i^\ast + 
\Lambda_i^\theta\cdot 0 + \Lambda_i^\alpha \alpha \leq \lambda_i$. Solving this we obtain the 
minimal value $\alpha_{\min} = 1.7555$ and the MRPI sets shown in Figure~\ref{fig:minimal:scaling:comparison:MRPIs}.
The computation terminates after seven iterations and produces a polyhedron $\mathcal Z^\infty$ supported by $m_\infty=10$
planes.
Caution is advised when interpreting $\alpha>0$, since the system is nonlinear extrapolations reveal very
little insight, the only information we can safely extract is that the current set of inputs $\mathcal U(0)=\mathcal U$ 
is not large enough to cope with the perturbation set given by upper bounds of the nonlinear effects.
%
%
\begin{figure}
\begin{lpic}{minimalAlphaForConstantDisturbance(.65,)}
{\tiny
\lbl[r]{7,87;$1.5$}
\lbl[r]{7,69;$1$}
\lbl[r]{7,51;$0.5$}
\lbl[r]{7,34;$0$}
\lbl[r]{7,16;$-0.5$}
\lbl[t]{15,2;$-0.06$}
\lbl[t]{27,2;$-0.05$}
\lbl[t]{39,2;$-0.04$}
\lbl[t]{51,2;$-0.03$}
\lbl[t]{63,2;$-0.02$}
\lbl[t]{75,2;$-0.01$}
\lbl[t]{89,2;$0$}
\lbl[t]{100,2;$0.01$}
\lbl[t]{113,2;$0.02$}
}
{\footnotesize
\lbl[r]{5,45,90;$\tilde x_2$}
\lbl[t]{121,3;$\tilde x_1$}
}
\lbl[l]{93,32;$\longleftarrow\mathcal X^\infty$}
\lbl[r]{68,43;$\mathcal Z^\infty\vert_{(\alpha_{\min},0)}\longrightarrow$}
\end{lpic}
\caption{Minimal scaling for MRPI set computed for constant disturbance which contains
 MRPI set for piecewise affine disturbances is $\alpha=1.7555$. Note that since the nonlinearities of the system
 dynamics are not symmetrical around the equilibrium the MRPI set with fixed constraints on the disturbance
 is non-symmetric.}
 \label{fig:minimal:scaling:comparison:MRPIs}
\end{figure}

In the second example, we compute the parametrised MRPI set for the system

@@

\underbrace{\left(\begin{array}{cc} 1 & 2 \\ 2 & 1 \end{array}\right)}_D w.

@@

All constraints were mainly chosen to be illustrative.

@@

(\theta)\wedge \alpha,\theta>-{\bf{1}}\right\}$, with $K$ and $K_w$ being the solution to the aforementioned semidefinite program

@@

We use $Q = \text{diag}(2,1)$ and $R = I$. Using these numerical values we determine the MRPI set 
$\mathcal Z^\infty$. After 22 iterations the algorithm terminates producing a total of 61 facets. 
Notice that we not only know the sign of the elements of $\mathcal H$, but we also know that each facet of $\mathcal Z(x,\theta,\alpha)$
depends at most on one $\alpha_i$, the algorithm does not affect the elements corresponding on $\alpha$ and reduction
methods can not reduce rows depending on two individual variables, therefore we know that $\Lambda^\alpha$ will have at 
most one nonzero entry per row. We can therefore 
compute which $\alpha_i$ will change the MRPI set the most. This can be done by element wise calculating

@@

Analogous to the first example we might want to know how much disturbance the closed loop system can 
take such that a given set is contained in the MRPI set $\mathcal C\subseteq\mathcal Z^\infty\vert_{(\theta,0)}$.
